A thermodynamic view of dusty protoplanetary disks I: axisymmetric stability

### 2017-01-04 summary.tex
note to self in 9.4.1 on possibility of dusty gravito-turbulence, because dust-gas drift is like energy sink

>>>>

Another potential connection to previous results for gas disks is  
gravito-turbulence. Cooling, self-gravitating gaseous disks 
sustain a turbulent state where shock heating due to gravitational 
instabilities are balanced by thermal losses
\citep{gammie01}. Now, dust-gas drift behaves like thermal diffusion
or cooling (Eq. \ref{eff_energy}), similar to how radiative cooling 
appears in models of gravito-turbulent disks. Thus it may be
conceivable that a massive dusty disk admit `dusty
gravito-turbulence'.
